In the following benchmarks a number of hyper parameters were used to
determine the training data that derive accuracy values with the
earthquake benchmark code.

All time data is grouped into 2 week time periods.

We distinguish the following abbreviations. The first term defines the
start point and we used the values

{\em Now} means the first training time period starts at the current
date,

2 weeks means the first training time period starts at 2 weeks before
the current date,

3M means the first training time period starts at 3 months before the
current date,

6M means the first training time period starts at 6 months before the
current date,

1Y means the first training time period starts at 1 year before the
current date.

The second parameter has two values 2wk+xAVG where x is a number. The
first defines a 2 week time period denoted by 2wk. The second defines
how many total time groups are put in the training data.

In addition we also have the values

3 Months Back means the first and only training time period starts at 3 months before the current date.

Year Back means the first and only training time period starts at 1 year before the current date.

2 weeks Now means the first and only training time period starts at the current date.

\begin{description}
\item {\bf Now 2wk+26AVG} -- 2 week training time periods starting at
  the current date and ending either after 26 total time periods are
  reached.
\item {\bf Now 2wk+13AVG} -- 2 week training time periods starting at
  the current date and ending either after 13 total time periods are
  reached.
\item {\bf Now 2wk+7AVG} -- 2 week training time periods starting at
  the current date and ending either after 7 total time periods are
  reached.
\item {\bf 2 weeks Now} -- 2 week training time periods starting at
  the current date and ending after 1 time period is reached.
\item {\bf 3M 2wk+26AVG} -- 2 week training time periods starting at 3
  months before the current date and ending either after 26 total time
  periods are reached.
\item {\bf 3M 2wk+13AVG} -- 2 week training time periods starting at 3
  months before the current date and ending either after 13 total time
  periods are reached.
\item {\bf 3M 2wk+7AVG} -- 2 week training time periods starting at 3
  months before the current date and ending either after 7 total time
  periods are reached.
\item {\bf 1Y 2wk+26AVG} -- 2 week training time periods starting at 1
  year before the current date and ending either after 26 total time
  periods are reached.
\item {\bf 6M 2wk+26AVG} -- 2 week training time periods starting at 6
  months before the current date and ending either after 26 total time
  periods are reached.
\item {\bf 6M 2wk+13AVG} -- 2 week training time periods starting at 6
  months before the current date and ending either after 13 total time
  periods are reached.
\item {\bf 1Y 2wk+13AVG} -- 2 week training time periods starting at 1
  year before the current date and ending either after 13 total time
  periods are reached.
\item {\bf 6M 2wk+7AVG} -- 2 week training time periods starting at 6
  months before the current date and ending either after 7 total time
  periods are reached.
\item {\bf 6 Months Back} -- 2 week training time periods starting at
  6 months before the current date and ending after 1 time period is
  reached.
\item {\bf 1Y 2wk+7AVG} -- 2 week training time periods starting at 1
  year before the current date and ending either after 7 total time
  periods are reached.
\item {\bf Year Back} -- 2 week training time periods starting at 1
  year before the current date and ending after 1 time period is
  reached.
\item {\bf 3 Months Back} -- 2 week training time periods starting at
  3 months before the current date and ending after 1 time period is
  reached.
\end{description}



